---
title: On the marginal value of swimming in woodland caribou
author:
  - name: Quinn M.R. Webber
    institute: cabe
    correspondence: true
  - name: Jack G. Hendrix
    institute: cabe
  - name: Alec L. Robitaille
    email: robit.alec@gmail.com
    institute: bio
  - name: Eric Vander Wal
    institute: [bio, cabe]
institute: 
  - bio: Department of Biology, Memorial University of Newfoundland, Canada
  - cabe: Cognitive and Behavioural Ecology Interdisciplinary Program, Memorial University of Newfoundland 
output:
   bookdown::word_document2:
     reference_docx: template.docx
     pandoc_args:
      - '--lua-filter=scholarly-metadata.lua'
      - '--lua-filter=author-info-blocks.lua'
bibliography: ../references/swim.bib
csl: ecology.csl
---


```{r knitropts, include = FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      eval = TRUE,
                      fig.align = 'center')
```


```{r pkgs}
library(data.table)
```




|  			Habitat 			type 		        |  			Description 		     |  			Common 			species and groups of species 		        |
|-|-|-|
|  			Lichen 		     |  			A 			non-forested shrub-dominated habitat found on hummocky terrain and 			may have thin soils with exposed bedrock, ericaceous shrubs 			dominate having relatively high percent cover. Tree species are 			always stunted and rarely grow above the shrub layer. The herb 			layer is species-rich, is nearly always dominated by ground 			lichen. 		                       |  			Caribou 			lichen (Cladonia sp.)  			  			Sheep 			laurel (Kalmia sp.)  			  			Dwarf 			willow (Salix herbacea) 		                          |
|  			Wetland 		     |  			Characterized 			by open or ponded water. Dominated by aquatic and submergent 			vegetation such as yellow pond lily and rushes. 		           |  			Sedges 			(Carex sp.)  			  			Rushes 			(Juncus sp.)  			  			Mosses 		                       |
|  			Conifer 			forest 		        |  			Dominant 			tree species are typically balsam fir or black spruce with lesser 			amount of larch, ericaceous shrubs are found in this habitat and 			sheep laurel. 		              |  			White 			spruce (Picea glauca)  			  			Black 			spruce (Picea mariana)  			  			Balsam 			fir (Abies balsamea)  			  			Larch 			(Larix laricina) 		                                   |
|  			Rocky 			barrens 		        |  			Windswept 			with thin layer that is comprised of bedrock, exposed soil, stone, 			and boulders. The shrub layer is composed mainly of ericaceous 			shrubs. Ground cover consists of grasses, lichens, mosses, and 			smaller berry plants. 		                 |  			Alder 			(Alnus sp.)  			  			Sheep 			laurel (Kalmia sp.)  			  			Crowberry 			(Empetrum nigrum)  			  			Vaccinium 			sp. 		                                   |